---
title: "CS225_data_cleaning"
author: "JialongLi"
date: "11/13/2022"
output: html_document
---
# Data Cleaning and input "Latitude" and "Longitude data" by hand

```{r setup, include=FALSE}
# import necessary packages
library(tidyverse)
library(stringr)
library(readxl)
library(data.table)
```

```{r read data}
# read raw data
data_1k <- read_excel("1-1000.xls")
data_2k <- read_excel("1001-2000.xls")
data_3k <- read_excel("2001-3000.xls")

# select cols that we need
data_select_1k = data_1k |>
  select(Affiliations) |>
  drop_na()

data_select_2k = data_2k |>
  select(Affiliations) |>
  drop_na()


dim(data_select_1k)
dim(data_select_2k)
```

```{r}
# data_select <- rbind(data_select_1k, data_select_2k)
data_select = data_select_1k
dim(data_select)
```

```{r}
# string split 
After_split = data_select$Affiliations |>
  str_split(";", simplify = TRUE)

Afflication_df = as.data.frame(After_split)

data_select$First = Afflication_df[,1]
data_select$Second = Afflication_df[,2]
data_select$Third = Afflication_df[,3]
data_select$Fourth = Afflication_df[,4]
data_select$Fifth = Afflication_df[,5]

data_select$Second = sub('.', '', data_select$Second)
data_select$Third = sub('.', '', data_select$Third)
data_select$Fourth = sub('.', '', data_select$Fourth)
data_select$Fifth = sub('.', '', data_select$Fifth)


# all systems
output_1 = data_select |>
  select(First, `Times Cited, WoS Core`) |>
  #filter((First %like% "Univ") | (First %like% "Inst") | (First %like% "College")) |>
  arrange(desc(`Times Cited, WoS Core`)) |>
  rename(School = First)
output_cleaned_1 = output_1 |>
  filter((!School %like% 'System') & (School != "Purdue University")  & (School != "Pennsylvania State University")  & (School != "University of North Carolina") & (School != "Arizona State University") & (School != "Indian Statistical Institute") & (School != "University of Washington") & (!School %like% "Medical School") & (!School %like% 'School of'))

output_2 = data_select |>
  select(Second, `Times Cited, WoS Core`) |>
  #filter((Second %like% "Univ") | (Second %like% "Inst") | (Second %like% "College")) |>
  arrange(desc(`Times Cited, WoS Core`)) |>
  rename(School = Second)
output_cleaned_2 = output_2 |>
  filter((!School %like% 'System') & (School != "Purdue University")  & (School != "Pennsylvania State University")  & (School != "University of North Carolina") & (School != "Arizona State University") & (School != "Indian Statistical Institute") & (School != "University of Washington") & (!School %like% "Medical School") & (!School %like% 'School of'))

output_3 = data_select |>
  select(Third, `Times Cited, WoS Core`) |>
  #filter((Third %like% "Univ") | (Third %like% "Inst") | (Third %like% "College")) |>
  arrange(desc(`Times Cited, WoS Core`)) |>
  rename(School = Third)
output_cleaned_3 = output_3 |>
  filter((!School %like% 'System') & (School != "Purdue University")  & (School != "Pennsylvania State University")  & (School != "University of North Carolina") & (School != "Arizona State University") & (School != "Indian Statistical Institute") & (School != "University of Washington") & (!School %like% "Medical School") & (!School %like% 'School of'))

output_4 = data_select |>
  select(Fourth, `Times Cited, WoS Core`) |>
  #filter((Fourth %like% "Univ") | (Fourth %like% "Inst") | (Fourth %like% "College")) |>
  arrange(desc(`Times Cited, WoS Core`)) |>
  rename(School = Fourth)
output_cleaned_4 = output_4 |>
  filter((!School %like% 'System') & (School != "Purdue University")  & (School != "Pennsylvania State University")  & (School != "University of North Carolina") & (School != "Arizona State University") & (School != "Indian Statistical Institute") & (School != "University of Washington") & (!School %like% "Medical School") & (!School %like% 'School of'))

output_5 = data_select |>
  select(Fifth, `Times Cited, WoS Core`) |>
  #filter((Fifth %like% "Univ") | (Fifth %like% "Inst") | (Fifth %like% "College")) |>
  arrange(desc(`Times Cited, WoS Core`)) |>
  rename(School = Fifth)
output_cleaned_5 = output_5 |>
  filter((!School %like% 'System') & (School != "Purdue University")  & (School != "Pennsylvania State University")  & (School != "University of North Carolina") & (School != "Arizona State University") & (School != "Indian Statistical Institute") & (School != "University of Washington") & (!School %like% "Medical School") & (!School %like% 'School of'))

output_total <- rbind(output_cleaned_1, output_cleaned_2, output_cleaned_3, output_cleaned_4, output_cleaned_5)

droped_output = output_total |> 
  filter(School %like% "Univ" | School %like% "College" | School %like% "Institu") |>
  group_by(`School`) |>
  summarise(times = n()) |>
  arrange(desc(times)) 
```


```{r}
droped_output
droped_output$School[1]
droped_output$School[1:262] = str_replace_all(droped_output$School[1:262], "( )", "_")
write.table(droped_output, "data_vertex_262.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
```

```{r}
edge_builder = data_select |>
  select(-c(Affiliations, `Times Cited, WoS Core`))
```

## deduplication
For example, Purdue University System; Purdue University; Purdue University West Lafayette Campus is literally point to one university, but it appears 3 times.
Where we want to remove:

University of Minnesota System
University of Illinois System
University of California System
University System of Georgia
Indiana University System
University System of Maryland
Arizona State University
State University System of Florida
Louisiana State University System
Purdue University System
University of Michigan System
University of Texas System
University of Massachusetts System
University of Nebraska System
University System of Ohio
University of South Carolina System
Indian Institute of Management (IIM System)
Purdue University
Pennsylvania Commonwealth System of Higher Education (PCSHE)
University of Alabama System
Pennsylvania State University
Southern Illinois University System
University of Hawaii System
Texas A&M University System
Louisiana State University System
University of Houston System
University of North Carolina
University of Maine System
University of Alabama System
Auburn University System
Pennsylvania State University
Indian Statistical Institute
University of Tennessee System
University of North Carolina

-> I can do this by regex, but It's more safety to check it by eye first.

```{r}
edge_builder
```


```{r}
dim(edge_builder)
# (607, 5)

# delete them -> overwrite by "" (all cols)
for (i in 1:607) {
  for (j in 1:5) {
  if (edge_builder[i,j] %like% 'System' | edge_builder[i,j] %like% 'School of' |  edge_builder[i,j] %like% "Medical School" | edge_builder[i,j] == "Purdue University" | edge_builder[i,j] == "Pennsylvania State University" | edge_builder[i,j] == "University of North Carolina" | edge_builder[i,j] == "Indian Statistical Institute" | edge_builder[i,j] == "Arizona State University" | edge_builder[i,j] == "University of Washington") {
    edge_builder[i,j] = ""
    }
  }
}
  
edge_builder

# MRC Biostatistics Unit
# Harvard T.H. Chan School of Public Health	
```

```{r}
# how many universities left in each layers
edge_builder |>
  filter(First != "") |>
  nrow()
edge_builder |>
  filter(Second != "") |>
  nrow()
edge_builder |>
  filter(Third != "") |>
  nrow()
edge_builder |>
  filter(Fourth != "") |>
  nrow()
edge_builder |>
  filter(Fifth != "") |>
  nrow()
# we' ll only keep papers that have <= 5 writers.
```


```{r}
# transfer the 19 df with features to df with 2 features.
# Which is how the "edge" works.
removed_df = edge_builder

# push value into result, (1 & 2)
result_1 <- data.frame(matrix(nrow = 7000, ncol = 2))


# 1 & 2
for (i in 1:607) {
  if (removed_df[[i,1]] != "" & removed_df[[i,2]] != "") {
    result_1$X1[[i]] = removed_df[[i,1]]
    result_1$X2[[i]] = removed_df[[i,2]]
  }
}

# 1 & 3
for (i in 1:607) {
  if (removed_df[[i,1]] != "" & removed_df[[i,3]] != "") {
    result_1$X1[[i+607]] = removed_df[[i,1]]
    result_1$X2[[i+607]] = removed_df[[i,3]]
  }
}

# 1 & 4
for (i in 1:607) {
  if (removed_df[[i,1]] != "" & removed_df[[i,4]] != "") {
    result_1$X1[[i+607*2]] = removed_df[[i,1]]
    result_1$X2[[i+607*2]] = removed_df[[i,4]]
  }
}

# 1 & 5
for (i in 1:607) {
  if (removed_df[[i,1]] != "" & removed_df[i,5] != "") {
    result_1$X1[[i+607*3]] = removed_df[[i,1]]
    result_1$X2[[i+607*3]] = removed_df[[i,5]]
  }
}

# 2 & 3
for (i in 1:607) {
  if (removed_df[[i,2]] != "" & removed_df[[i,3]] != "") {
    result_1$X1[[i+607*4]] = removed_df[[i,2]]
    result_1$X2[[i+607*4]] = removed_df[[i,3]]
  }
}

# 2 & 4
for (i in 1:607) {
  if (removed_df[[i,2]] != "" & removed_df[[i,4]] != "") {
    result_1$X1[[i+607*5]] = removed_df[[i,2]]
    result_1$X2[[i+607*5]] = removed_df[[i,4]]
  }
}

# 2 & 5
for (i in 1:607) {
  if (removed_df[[i,2]] != "" & removed_df[[i,5]] != "") {
    result_1$X1[[i+607*6]] = removed_df[[i,2]]
    result_1$X2[[i+607*6]] = removed_df[[i,5]]
  }
}

# 3 & 4
for (i in 1:607) {
  if (removed_df[[i,3]] != "" & removed_df[[i,4]] != "") {
    result_1$X1[[i+607*7]] = removed_df[[i,3]]
    result_1$X2[[i+607*7]] = removed_df[[i,4]]
  }
}

# 3 & 5
for (i in 1:607) {
  if (removed_df[[i,3]] != "" & removed_df[[i,5]] != "") {
    result_1$X1[[i+607*8]] = removed_df[[i,3]]
    result_1$X2[[i+607*8]] = removed_df[[i,5]]
  }
}

# 4 & 5
for (i in 1:607) {
  if (removed_df[[i,4]] != "" & removed_df[[i,5]] != "")
    result_1$X1[[i+607*9]] = removed_df[[i,4]]
    result_1$X2[[i+607*9]] = removed_df[[i,5]]
}

result_1
```

```{r}
result_droped = result_1 |>
  drop_na() |> 
  filter( (X1 %like% "Univ" | X1 %like% "College" | X1 %like% "Institu") & (X2 %like% "Univ" | X2 %like% "College" | X2 %like% "Institu")) |>
  arrange(X1)

result_droped$X1[1:617] = str_replace_all(result_droped$X1[1:617], "( )", "_")
result_droped$X2[1:617] = str_replace_all(result_droped$X2[1:617], "( )", "_")

write.table(result_droped, "data_edge_617.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
```

```{r}
# test case 0 -> special test
# if universities only coop with themselves

vertex_0 = c("UIUC", "Purdue")
coop_0 = c("UIUC", "UIUC", "UIUC")

edge_1 = c("UIUC", "UIUC")
edge_2 = c("UIUC", "UIUC")
edge_3 = c("UIUC", "UIUC")

test_vertex_0 = t(t(vertex_0))
test_edge_0 = t(cbind(edge_1, edge_2, edge_3))

write.table(test_vertex_0, "data_vertex_test0.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
write.table(test_edge_0, "data_edge_test0.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")

# The connect component should be 2.
```


```{r}
# test case 1 -> simple
vertex_1 = c("UIUC", "Purdue", "NU", "UChicago")
coop_1 = c("UIUC", "NU", "Purdue")
coop_2 = c("NU", "Purdue")

edge_1 = c("UIUC", "NU")
edge_2 = c("UIUC", "Purdue")
edge_3 = c("NU", "Purdue")
edge_4 = c("NU", "Purdue")

test_vertex_1 = t(t(vertex_1))
test_edge_1 = t(cbind(edge_1, edge_2, edge_3, edge_4))

write.table(test_vertex_1, "data_vertex_test1.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
write.table(test_edge_1, "data_edge_test1.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
```

```{r}
# test case 2 -> complex
vertex_2 = c("UIUC", "Purdue", "NU", "UChicago", "Harvard", "MIT", "U_of_T")
coop_1 = c("UIUC", "NU", "Purdue", "MIT","UIUC")
coop_2 = c("Purdue","NU","MIT")
coop_3 = c("UChicago", "NU")
coop_4 = c("Harvard", "Harvard")

# extract UIUC_1
edge_a1 = c("UIUC", "NU")
edge_a2 = c("UIUC", "Purdue")
edge_a3 = c("UIUC", "MIT") 
edge_a4 = c("UIUC", "UIUC")

# extract UIUC_2
edge_a5 = c("UIUC", "NU")
edge_a6 = c("UIUC", "Purdue")
edge_a7 = c("UIUC", "MIT") 
edge_a8 = c("UIUC", "UIUC")

# extract NU
edge_b1 = c("NU", "UIUC")
edge_b2 = c("NU", "Purdue")
edge_b3 = c("NU", "MIT") 
edge_b4 = c("NU", "UIUC") 
edge_b5 = c("NU", "Purdue")
edge_b6 = c("NU", "MIT")
edge_b7 = c("NU", "UChicago")

# extract Purdue
edge_c1 = c("Purdue", "UIUC")
edge_c2 = c("Purdue", "NU")
edge_c3 = c("Purdue", "MIT")
edge_c4 = c("Purdue", "UIUC")
edge_c5 = c("Purdue", "NU")
edge_c6 = c("Purdue", "MIT")

# extract MIT
edge_d1 = c("MIT", "UIUC")
edge_d2 = c("MIT", "NU")
edge_d3 = c("MIT", "Purdue")
edge_d4 = c("MIT", "UIUC")
edge_d5 = c("MIT", "Purdue")
edge_d6 = c("MIT", "NU")

# extract UChicago
edge_e1 = c("UChicago", "NU")

# extract UChicago
edge_f1 = c("Harvard", "Harvard")

# write out
test_vertex_2 = t(t(vertex_2))
test_edge_2 = t(cbind(edge_a1,edge_a2,edge_a3,edge_a4,edge_a5,edge_a6,edge_a7,edge_a8,edge_b1,edge_b2,edge_b3,edge_b4,edge_b5,edge_b6,edge_b7,edge_c1,edge_c2,edge_c3,edge_c4,edge_c5,edge_c6,edge_d1,edge_d2,edge_d3,edge_d4,edge_d5,edge_d6,edge_e1,edge_f1))


write.table(test_vertex_2, "data_vertex_test2.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
write.table(test_edge_2, "data_edge_test2.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")

# connected component should be 3
```

```{r}
# test betweeness
# suppose in a subgraph, there are 6 schools

BC_test_0 = c("UIUC", "UCLA", "Duke", "Rice", "Yale", "UCSD")

BC_edge_a1 = c("UIUC", "UCLA")
BC_edge_a2 = c("UIUC", "Duke")
BC_edge_a3 = c("Duke", "Yale")
BC_edge_a4 = c("Duke", "Rice")

BC_edge_a5 = c("Yale", "Rice")
BC_edge_a6 = c("Yale", "UCSD")
BC_edge_a7 = c("Rice", "UCSD")
BC_edge_a8 = c("Rice", "UCLA")

# a = 1.5 UCLA
# b = 2.5 Rice
# c = 2.5 Yale
# d = 0 UCSD
# e = 1 UIUC
# f = 1.5 Duke

BC_test_vertex_0 = t(t(BC_test_0))
BC_test_edge_0 = t(cbind(BC_edge_a1,BC_edge_a2,BC_edge_a3,BC_edge_a4,BC_edge_a5,BC_edge_a6,BC_edge_a7))


write.table(BC_test_vertex_0, "data_BC_vertex_test0.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
write.table(BC_test_edge_0, "data_BC_edge_test0.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
```

```{r}
# test betweeness
# suppose in a subgraph, there are 6 schools

BC_test_1 = c("UIUC", "Duke", "Rice", "Yale", "UCSD")

BC_edge_b1 = c("UIUC", "Duke")
BC_edge_b2 = c("Duke", "Yale")
BC_edge_b3 = c("Duke", "Rice")
BC_edge_b4 = c("Yale", "Rice")
BC_edge_b5 = c("Yale", "UCSD")
BC_edge_b6 = c("UCSD", "Rice")

BC_test_vertex_1 = t(t(BC_test_1))
BC_test_edge_1 = t(cbind(BC_edge_b1,BC_edge_b2,BC_edge_b3,BC_edge_b4,BC_edge_b5,BC_edge_b6))

write.table(BC_test_vertex_1, "data_BC_vertex_test1.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
write.table(BC_test_edge_1, "data_BC_edge_test1.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
```

```{r}
# test betweeness
# suppose in a subgraph, there are 6 schools

BC_test_2 = c("UIUC", "UChicago", "NU", "Yale", "Purdue", "Harvard")

BC_edge_c1 = c("UIUC", "UChicago")
BC_edge_c2 = c("UChicago", "Yale")
BC_edge_c3 = c("Yale", "UIUC")
BC_edge_c4 = c("UIUC", "NU")
BC_edge_c5 = c("NU", "Purdue")
BC_edge_c6 = c("NU", "Harvard")
BC_edge_c7 = c("Purdue", "Harvard")

BC_test_vertex_2 = t(t(BC_test_2))
BC_test_edge_2 = t(cbind(BC_edge_c1,BC_edge_c2,BC_edge_c3,BC_edge_c4,BC_edge_c5,BC_edge_c6,BC_edge_c7))

write.table(BC_test_vertex_2, "data_BC_vertex_test2.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
write.table(BC_test_edge_2, "data_BC_edge_test2.csv", row.names = FALSE, col.names = FALSE, quote = FALSE, sep = ",")
```


